Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-11-14 R0V0.tex
Add the single system expression and expand the paragraph on CLFs. Continue with ADMM formulation.

@@

The importance of the stability of \eqref{eq:general system:differential} for system \eqref{eq:general system} can be understood as follows. Given fixed controls $u$ and $\delta u$ for systems \eqref{eq:general system} and \eqref{eq:general system:differential}, respectively. If the norm of every solution $\Delta_x(t,x,\delta_x,u,\delta u)$ converges to zero exponentially, as the time tends to infinity, then every pair of solutions to \eqref{eq:general system} converge to each other exponentially. The interested reader may address \cite{Lohmiller1998,Sontag2010} and references therein for further details.

@@

\begin{definition}\label{def:}
		 A metric $V:\mathbb{R}^n\times\mathbb{R}^n\to\mathbb{R}_{\geq0}$ receives the adjective \emph{contraction} if for fixed controls $u$ and $\delta u$ for systems \eqref{eq:general system} and \eqref{eq:general system:differential}, respectively, there exists a value $\lambda>0$ such that the inequality
	 	 \begin{equation}
	 	 	\frac{dV}{dt}(X(t,x,u),\Delta(t,x,\delta x,u,\delta u))\leq -\lambda V(x,\delta_x)
 	 	 \end{equation}
 	 	 holds, for every pair $(x,\delta_x)\in\mathbb{R}^n\times\mathbb{R}^n$.
\end{definition}

@@

Based on \cite{Manchester2014a}, the energy function also provides a control-Lyapunov function for system~\eqref{eq:general system} which can be employed to design a distributed controller for system~\eqref{eq:general system}.

@@

The alternating direction method of multipliers (ADMM) provides a framework to solve the MI~\eqref{eq:MI formulation} in parallel \cite{BoydParikhChuEtAl2010,MeissenLessardArcakEtAl2015}. To use this framework, define the sets $\mathbf{Y}^n=\{Y\in\mathbb{R}^{m\times n}\}$, $\mathbf{S}_{\succ0}^n=\{W\in\mathbb{R}^{n\times n}:W\succ0,W=W^\top\}$, $\mathbf{T}=\{(W_1,\ldots,W_N,Y)\in \mathbb{R}^{n_i\times n_i}\times \mathbb{R}^{m\times n}:\mathbin{\mathtt{diag}}(W_1,\ldots,W_N),T\prec0\}$. For a set $\mathbf{G}$ define the indicator function $H:\{\mathbf{G}\}\times \mathbb{R}^k\to \{0\}\cup\{\infty\}$ as
\begin{equation*}
	H(\mathbf{G},g)=\begin{cases}
									0,&g\in \mathbf{G}\\
									\infty,&\text{Otherwise.}
								\end{cases}
\end{equation*}

The MI~\eqref{eq:MI formulation} can be cast into the following optimization problem
\begin{equation*}
	\begin{array}{rl}
		\text{minimize}&\displaystyle H(\mathbf{T},(Z_1,\ldots,Z_N,Z_{N+1}))+\sum_{i=1}^N H(\mathbf{S}_{\succ0}^{n_i},W_i)\\
		\text{subject to}&W_i-Z_i=0,\quad \forall i\in\mathbb{N}_{[1,N]}\\
		&Y-Z_{N+1}=0
	\end{array}
\end{equation*}

>>>>

Let $N>0$ be an integer, for each index $i\in\mathbb{N}_{[1,N]}$, system~\eqref{eq:general system} can be decomposed into smaller components as follows.
\begin{equation}\label{eq:subsystem}
	\dot{x}_i=f_i(x_i,\breve{x}_i)+b_i(x_i)u_i\;,
\end{equation}
where $\breve{x}_i\in\mathbb{R}^{\breve{n}_i}$ stands for the vector composed of states $x_j$ of systems that are adjacent to system~\eqref{eq:subsystem}.

@@

The importance of the stability of \eqref{eq:general system:differential} for system \eqref{eq:general system} can be understood as follows. Given fixed controls $u$ and $\delta u$ for systems \eqref{eq:general system} and \eqref{eq:general system:differential}, respectively. If the norm of every solution $\Delta_x(t,x,\delta_x,u,\delta_u)$ converges to zero exponentially, as the time tends to infinity, then every pair of solutions to \eqref{eq:general system} converge to each other exponentially. The interested reader may address \cite{Lohmiller1998,Sontag2010} and references therein for further details.

@@

\begin{definition}\label{def:}
		 A metric $V:\mathbb{R}^n\times\mathbb{R}^n\to\mathbb{R}_{\geq0}$ receives the adjective \emph{contraction} if for fixed controls $u$ and $\delta u$ for systems \eqref{eq:general system} and \eqref{eq:general system:differential}, respectively, there exists a value $\lambda>0$ such that the inequality
	 	 \begin{equation}
	 	 	\tfrac{dV}{dt}(X(t,x,u),\Delta(t,x,\delta_x,u,\delta_u))\leq -\lambda V(x,\delta_x)
 	 	 \end{equation}
 	 	 holds, for every pair $(x,\delta_x)\in\mathbb{R}^n\times\mathbb{R}^n$.
\end{definition}

@@

Based on \cite{Manchester2014a}, the energy function also provides a control-Lyapunov function for system~\eqref{eq:general system} that can be employed to design a distributed controller for system~\eqref{eq:general system}. More precisely, from the first variation of the energy function, the time derivative of $e$ yields the equation
\begin{align}
	\dfrac{1}{2}De^+(X^\ast,X)=\langle \gamma_s(t,0),\dot{X}^\ast\rangle_{X^\ast}-\langle \gamma_s(t,1),f(x)\rangle_{X}\nonumber\\
	-\langle \gamma_s(t,1),B(x)u\rangle_{X}\,\label{eq:CLF derivative}
\end{align}
where $De^+$ stands for the Dini's upper right-hand time derivative of the energy $e$ along the solutions $X$ and $X^\ast$. A distributed controller can be obtained by finding the appropriate feedback law for system~\eqref{eq:general system} rendering \eqref{eq:CLF derivative} negative definite. This can be achieved by noticing that \eqref{eq:CLF derivative} is the sum of $N$ terms of the form
\begin{align*}
	\tfrac{\partial \gamma_i}{\partial s_i}(t,0)M_i(X_i^\ast)X_i^\ast-\tfrac{\partial \gamma_i}{\partial s_i}(t,1)M_i(X_i)f_i(X_i,\breve{X}_i)\\
	-\tfrac{\partial \gamma_i}{\partial s_i}(t,1)M_i(X_i)B_i(X_i)u_i\;.
\end{align*}

@@

The alternating direction method of multipliers (ADMM) provides a framework to solve the MI~\eqref{eq:MI formulation} in a distributed fashion \cite{BoydParikhChuEtAl2010,MeissenLessardArcakEtAl2015}. To use this framework, define the sets $\mathbf{S}_{\succ0}^n=\{W\in\mathbb{R}^{n\times n}:W\succ0,W=W^\top\}$, $\mathbf{T}=\{Z\in D^{n\times n}:\exists Y\in\mathbb{R}^{m\times n}, T\prec0\}$. For a set $\mathbf{G}$ define the indicator function $H:\{\mathbf{G}\}\times \mathbb{R}^k\to \{0\}\cup\{\infty\}$ as
\begin{equation*}
	H(\mathbf{G},g)=\begin{cases}
									0,&g\in \mathbf{G}\\
									\infty,&\text{Otherwise.}
								\end{cases}
\end{equation*}

The MI~\eqref{eq:MI formulation} can be cast into the following optimization problem
\begin{equation*}
	\begin{array}{rl}
		\text{minimize}&\displaystyle H(\mathbf{T},Z)+\sum_{i=1}^N H(\mathbf{S}_{\succ0}^{n_i},W_i)\\
		\text{subject to}&\mathbin{\mathtt{diag}}(W_1,\ldots,W_N)-Z=0\;.
	\end{array}
\end{equation*}
The ADMM algorithm can be written as
\begin{equation*}
	\begin{array}{rl}
		W_i^{k+1}:=&\mathbin{\mathtt{argmin}}_{W_i}\left(H(\mathbf{S}_{\succ0}^{n_i},W_i))\right)
	\end{array}
\end{equation*}
